Analyzing the Effect of Surface in Tennis Grand Slams

### 2018-09-07 contest/surface-type/paper-tennis.Rmd
Adding some format stuff

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)
library(deuce)
library(dplyr)
library(ggplot2)
library(forcats)
library(stringr)
```

@@

## Data

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)
library(deuce)
library(dplyr)
library(ggplot2)
library(forcats)
library(stringr)
library(knitr)
library(kableExtra)
```

@@

## Data
The data consists of `r nrow(gs)` matches split evenly over the four grand slams and the two leagues (ATP and WTA).  Each match has `r ncol(gs)` attributes, many of which are redundant.  We focus on the following attributes for both the winner and loser of the match: games won, points won, retirement, break points faced, break points saved, aces, country of origin, and player attributes.  Additionally, we take into account the number of sets in a match, the surface type, minutes played, and round of the tournament.  A subset of the data is shown in Table \ref{tab:data}.

```{r tab-data, include = TRUE, echo = FALSE}
set.seed(19)
s_id <- which(gs$winner_name %in% c("Serena Williams", "Roger Federer", "Rafael Nadal"))
rand_inds <- sample(s_id, 5)
cols <- c("tourney_name", "year", "winner_ioc", "w_pointswon", "winner_name", "winner_rank", "l_pointswon", "loser_name")
knitr::kable(gs[rand_inds, cols], format = "latex",
             row.names = FALSE, col.names = c("Tournament", "Year", "W. Country", "W. Points", "Winner", "W. Rank", "L. Points", "Loser"),
             caption = "\\label{tab:data}Example of the grand slam data.  It includes winner and loser attributes, match attributes, and tournament attributes.  Not all attributes are shown here.",
             booktabs = TRUE) %>% kable_styling(latex_options = "striped")
```

### 2018-09-07 contest/surface-type/paper-tennis.tex
Adding some format stuff

@@

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}

@@

The data consists of 5080 matches split evenly over the four grand slams
and the two leagues (ATP and WTA). Each match has 82 attributes, many of
which are redundant. We focus on the following attributes for both the
winner and loser of the match: games won, points won, retirement, break
points faced, break points saved, aces, country of origin, and player
attributes. Additionally, we take into account the number of sets in a
match, the surface type, minutes played, and round of the tournament. A
subset of the data is shown in Table \ref{tab:data}.

\rowcolors{2}{gray!6}{white}
\begin{table}

\caption{\label{tab:tab-data}\label{tab:data}Example of the grand slam data.  It includes winner and loser attributes, match attributes, and tournament attributes.  Not all attributes are shown here.}
\centering
\begin{tabular}[t]{lrlrlrrl}
\hiderowcolors
\toprule
Tournament & Year & W. Country & W. Points & Winner & W. Rank & L. Points & Loser\\
\midrule
\showrowcolors
US Open & 2014 & USA & 58 & Serena Williams & 1 & 31 & Taylor Townsend\\
US Open & 2013 & ESP & 136 & Rafael Nadal & 2 & 112 & Philipp Kohlschreiber\\
Australian Open & 2015 & ESP & 91 & Rafael Nadal & 3 & 51 & Mikhail Youzhny\\
US Open & 2013 & USA & 65 & Serena Williams & 1 & 41 & Yaroslava Shvedova\\
Australian Open & 2017 & USA & 73 & Serena Williams & 2 & 60 & Lucie Safarova\\
\bottomrule
\end{tabular}
\end{table}
\rowcolors{2}{white}{white}
